Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-04-09 NovelLBM.tex
add corresponding author and smuggle in orcid

@@

\title{Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids}
\author{Richard Kellnberger$^1$, Tomasz Jüngst$^2$, Stephan Gekle$^1$}
\date{\today}
\begin{document}
	\maketitle

	\begin{center}
		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, Universität Bayreuth, Bayreuth, Germany\\
		$^2$ Department of Functional Materials in Medicine and Dentistry Institute of Functional Materials and Biofabrication (IFB) and KeyLab Polymers for Medicine of the Bavarian Polymer Institute (BPI) Universität Würzburg, Würzburg, Germany
	\end{center}
	\vspace{\fill}
	%TODO keywords

>>>>

\usepackage{orcidlink}

@@

\title{Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids}
\author{Richard Kellnberger$^{1\dagger}$\orcidlink{0009-0003-1782-4735}, Tomasz Jüngst$^2$, Stephan Gekle$^1$\orcidlink{0000-0001-5597-1160}}
\date{\today}
\begin{document}
	\maketitle

	\begin{center}
		$^1$ Biofluid Simulation and Modeling – Theoretische Physik VI, Universität Bayreuth, Bayreuth, Germany\\
		$^2$ Department of Functional Materials in Medicine and Dentistry Institute of Functional Materials and Biofabrication (IFB) and KeyLab Polymers for Medicine of the Bavarian Polymer Institute (BPI) Universität Würzburg, Würzburg, Germany
	\end{center}
	\begin{center}
		$^\dagger$ Corresponding author. Email: \href{mailto:Richard.Kellnberger@uni-bayreuth.de}{Richard.Kellnberger@uni-bayreuth.de}
	\end{center}
	\vspace{\fill}
	%TODO keywords
